---
title: "Getting started"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: '`r system.file("bibliography.bib", package = "pharmOncoX")`'
nocite: |
  @Kim2021-ye, @Freshour2021-bh, @Sioutos2007-nl, 
  @Ochoa2021-jc, @Nakken2023-ab
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<br><br>

# Installation

```{r install, echo = T, eval = F}

if (!("remotes" %in% installed.packages()) {
  install.packages("remotes")
}
remotes::install_github('sigven/pharmOncoX')
```

<br><br>

# Retrieval of drugs - examples 

## Get BRAF-targeted drugs, list records per indication


```{r braf_drugs_full, echo = T}
library(pharmOncoX)

## load the data
cache_dir <- tempdir()

drugs <- get_drugs(
  cache_dir = cache_dir,
  drug_targeted_agent = T,
	drug_target = c('BRAF'))

## Number of drug records
nrow(drugs$records)

## Column names of drug records
colnames(drugs$records)


```

<br><br>

## Get BRAF-targeted drugs, Open Targets Platform only, list per drug only

```{r braf_inhibitors, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  drug_targeted_agent = T,
  drug_action_inhibition = T,
	drug_target = c('BRAF'), 
  drug_source_opentargets = T, 
  output_resolution = "drug" )

drugs$records <- drugs$records |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable_braf_inhibitors <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt_braf_inhibitors, echo = F, eval = T}
dt_drugtable_braf_inhibitors
```

<br><br>

## Get immune checkpoint inhibitors, list per drug-target entry

```{r ici, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  drug_source_opentargets = F,
  drug_classified_cancer = T,
   output_resolution = "drug2target")

drugs$records <- drugs$records |>
  dplyr::filter(
    ((!is.na(atc_level3) & 
      atc_level3 == "PD-1/PDL-1 inhibitors") |
     (!is.na(target_symbol) &
      target_symbol == "CTLA4" |
      target_symbol == "TIGIT"))
  ) |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    ) |>
  dplyr::select(
    drug_id,
    drug_name,
    drug_type,
    target_symbol,
    target_genename,
    dplyr::everything()
  )

dt_drugtable_ici <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)
```

<br>

```{r dt_ici, echo = F, eval = T}
dt_drugtable_ici
```

<br><br>

## Get immune checkpoint inhibitors indicated for tumor subtypes within "Colon/Rectum", list per drug-target entry

```{r ici_colon, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  output_resolution = "drug2target", 
  drug_source_opentargets = T,
  drug_indication_main = "Colon/Rectum")

drugs$records <- drugs$records |>
  dplyr::filter(
     ((!is.na(atc_level3) & 
      atc_level3 == "PD-1/PDL-1 inhibitors") |
     (!is.na(target_symbol) &
      target_symbol == "CTLA4" |
      target_symbol == "TIGIT"))
  ) |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    ) |>
  dplyr::select(
    drug_id,
    drug_name,
    drug_type,
    target_symbol,
    target_genename,
    dplyr::everything()
  )

dt_drugtable_ici_colon <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt_ici_colon, echo = F, eval = T}
dt_drugtable_ici_colon
```

<br><br>

## Get antimetabolite drugs

```{r antimetabolites, echo = T}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  output_resolution = "drug")

drugs$records <- drugs$records |>
  dplyr::filter(
    stringr::str_detect(
      atc_level2, "ANTIMETABOLITES"
    )
  ) |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable_metabolites <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt_metabolites, echo = F, eval = T}
dt_drugtable_metabolites
```

<br><br>

## Get taxanes

```{r taxanes, echo = T}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  output_resolution = "drug")

drugs$records <- drugs$records |>
  dplyr::filter(
    stringr::str_detect(
      atc_level3, "Taxanes"
    )
  ) |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable_taxanes <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt_taxanes, echo = F, eval = T}
dt_drugtable_taxanes
```

<br><br>

## Get platinum compounds

```{r platins, echo = T}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  output_resolution = "drug")

drugs$records <- drugs$records |>
  dplyr::filter(
    stringr::str_detect(
      atc_level3, "Platinum compounds"
    )
  ) |>
  dplyr::select(
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable_platins <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt_platins, echo = F, eval = T}
dt_drugtable_platins
```

<br><br>

# Session Info

\vspace{5pt}
\footnotesize
```{r sessioninfo, eval = TRUE}
# set eval = FALSE if you don't want this info (useful for reproducibility) 
# to appear
sessionInfo()
```
\normalsize

<br><br>

# References