---
title: "Getting started"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: '`r system.file("bibliography.bib", package = "pharmOncoX")`'
nocite: |
  @Kim2021-ye, @Freshour2021-bh, @Sioutos2007-nl, 
  @Ochoa2021-jc, @Nakken2022-ab
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<br><br>

# Installation

```{r install, echo = T, eval = F}

if (!("remotes" %in% installed.packages()) {
  install.packages("remotes")
}
remotes::install_github('sigven/pharmOncoX')
```

<br><br>

# Retrieval of drugs - examples 

## Get BRAF-targeted drugs, list records per indication


```{r braf_drugs_full, echo = T}
library(pharmOncoX)

## load the data
cache_dir <- tempdir()

drugs <- get_drugs(
  cache_dir = cache_dir,
  drug_is_targeted = T,
	drug_target = c('BRAF'))

## Number of drug records
nrow(drugs$records)

## Column names of drug records
colnames(drugs$records)


```

<br><br>

## Get BRAF-targeted drugs, Open Targets Platform only, list per drug only

```{r braf_drugs, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  drug_is_targeted = T,
	drug_target = c('BRAF'), 
  source_opentargets_only = T, 
  output_resolution = "drug" )

drugs$records <- 
  dplyr::select(
    drugs$records,
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable1 <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt1, echo = F, eval = T}
dt_drugtable1
```

<br><br>

## Get immune checkpoint inhibitors, list per drug-target entry

```{r immune_checkpoint_inhibitors, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  is_immune_checkpoint_inhibitor = T,
   output_resolution = "drug2target")

drugs$records <- 
  dplyr::select(
    drugs$records,
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    ) |>
  dplyr::select(
    drug_id,
    drug_name,
    drug_type,
    target_symbol,
    target_genename,
    dplyr::everything()
  )

dt_drugtable2 <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)
```

<br>

```{r dt2, echo = F, eval = T}
dt_drugtable2
```

<br><br>

## Get immune checkpoint inhibitors indicated for tumor subtypes within "Colon/Rectum", list per drug-target entry

```{r immune_colon, echo = T, eval = T, results = "hide"}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  is_immune_checkpoint_inhibitor = T,
  output_resolution = "drug2target", 
  drug_indication_main = "Colon/Rectum")

drugs$records <- 
  dplyr::select(
    drugs$records,
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    ) |>
  dplyr::select(
    drug_id,
    drug_name,
    drug_type,
    target_symbol,
    target_genename,
    dplyr::everything()
  )

dt_drugtable3 <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt3, echo = F, eval = T}
dt_drugtable3
```

<br><br>

## Get antimetabolite drugs

```{r antimetabolites, echo = T}

drugs <- get_drugs(
  cache_dir = cache_dir, 
  is_antimetabolite = T,
  output_resolution = "drug")

drugs$records <- 
  dplyr::select(
    drugs$records,
    -c("drug_alias",
       "disease_main_group",
       "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|",", ")
    )

dt_drugtable4 <- DT::datatable(
  drugs$records,
  escape = FALSE,
  extensions = c("Buttons", "Responsive"), 
  width = "100%",
  options = list(
    buttons = c("csv", "excel"), 
    dom = "Bfrtip")
)

```

<br>

```{r dt4, echo = F, eval = T}
dt_drugtable4
```

<br><br>

# Session Info

\vspace{5pt}
\footnotesize
```{r sessioninfo, eval = TRUE}
# set eval = FALSE if you don't want this info (useful for reproducibility) 
# to appear
sessionInfo()
```
\normalsize

<br><br>

# References