---
title: "Getting started"
format:
  html:
    toc: true
    toc-depth: 2
knitr:
  opts_chunk:
    collapse: true
    comment: "#>"
execute:
  freeze: false
bibliography: "../inst/bibliography.bib"
nocite: |
  @Kim2021-ye, @Sioutos2007-nl,
  @Ochoa2021-jc, @Nakken2023-ab, @Griffith2017-do,
  @Tamborero2018-aj
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false

## install and load pharmOncoX package
if (!("remotes" %in% installed.packages())) {
 install.packages("remotes")
}
remotes::install_github('sigven/pharmOncoX')

library(pharmOncoX)
cache_dir <- tempdir()
```

```{r}
#| label: rt-helpers
#| include: false

## ── reactable helpers ────────────────────────────────────────────────────────

build_rt_row_details <- function(
    primary_cols,
    styling_cols = character(0),
    font_size = "0.94em") {
  exclude_cols <- c(".details", primary_cols, styling_cols)
  exclude_js   <- paste0("'", exclude_cols, "'", collapse = ", ")

  reactable::JS(paste0(
    "function(rowInfo) {",
    "  var exclude = [", exclude_js, "];",
    "  var items = Object.entries(rowInfo.row)",
    "    .filter(function(e) {",
    "      return exclude.indexOf(e[0]) === -1",
    "        && e[1] !== null && e[1] !== ''",
    "        && String(e[1]).length > 0;",
    "    })",
    "    .map(function(e) {",
    "      return '<div style=\"margin-bottom:8px;\">'",
    "           + '<div style=\"font-weight:600;color:#888;",
    "font-size:", font_size, ";text-transform:uppercase;",
    "letter-spacing:0.03em;margin-bottom:1px;\">'",
    "           + e[0] + '</div>'",
    "           + '<div style=\"color:#333;\">' + e[1] + '</div>'",
    "           + '</div>';",
    "    })",
    "    .join('');",
    "  if (!items) return null;",
    "  return '<div style=\"padding:10px 16px 12px 40px;background:#f9f9fb;",
    "display:flex;flex-wrap:wrap;gap:4px 24px;",
    "font-size:", font_size, ";\">' + items + '</div>';",
    "}"
  ))
}

rt_theme <- function() {
  reactable::reactableTheme(
    style = list(fontFamily = "inherit"),
    headerStyle = list(
      background    = "#2c313c",
      color         = "white",
      fontWeight    = "bold",
      fontSize      = "0.97em",
      padding       = "10px 14px",
      borderRight   = "1px solid rgba(255,255,255,0.3)",
      display       = "flex",
      alignItems    = "center"
    ),
    cellStyle = list(borderRight = "1px solid #e8e8e8"),
    searchInputStyle = list(borderColor = "#2c313c")
  )
}

## Convenience wrapper: hides every column not listed in col_defs_primary.
## If search_cols is supplied, a hidden-but-searchable SEARCH_INDEX column is
## prepended by pasting those fields together (missing columns are silently
## skipped via intersect()).
bake_reactable <- function(df,
                           col_defs_primary,
                           primary_cols,
                           styling_cols = character(0),
                           search_cols  = character(0)) {

  ## Build SEARCH_INDEX from whichever search_cols are present in df
  avail_search <- intersect(search_cols, colnames(df))
  if (length(avail_search) > 0) {
    df[["SEARCH_INDEX"]] <- apply(
      df[, avail_search, drop = FALSE], 1,
      function(row) {
        vals <- as.character(row)
        vals <- vals[!is.na(vals) & nchar(vals) > 0]
        paste(vals, collapse = " | ")
      }
    )
  }

  col_defs <- col_defs_primary

  ## SEARCH_INDEX: invisible in the table and in row-detail expansion,
  ## but picked up by reactable's global search box
  if ("SEARCH_INDEX" %in% colnames(df)) {
    col_defs[["SEARCH_INDEX"]] <- reactable::colDef(
      show = FALSE, searchable = TRUE)
  }

  for (col in colnames(df)) {
    if (!col %in% names(col_defs)) {
      col_defs[[col]] <- reactable::colDef(show = FALSE)
    }
  }

  ## Keep SEARCH_INDEX out of the row-detail card (it's a derivative column)
  details_styling <- unique(c(
    styling_cols,
    if ("SEARCH_INDEX" %in% colnames(df)) "SEARCH_INDEX" else character(0)
  ))

  reactable::reactable(
    df,
    columns        = col_defs,
    defaultColDef  = reactable::colDef(html = TRUE),
    details        = build_rt_row_details(
                       primary_cols = primary_cols,
                       styling_cols = details_styling),
    searchable     = TRUE,
    filterable     = TRUE,
    striped        = TRUE,
    highlight      = TRUE,
    compact        = TRUE,
    wrap           = TRUE,
    defaultPageSize = 10,
    theme          = rt_theme()
  )
}

## Columns to suppress completely (IDs, raw codes, internal flags)
## — excluded from both the main table view and the row-detail expansion
drug_base_styling_cols <- c(
  "drug_id", "molecule_chembl_id", "nci_t",
  "atc_code_level1", "atc_code_level2", "atc_code_level3",
  "atc_treatment_category", "inhibition_moa",
  "drug_frac_cancer_indications", "drug_approved_noncancer",
  "is_adc", "opentargets"
)

## Fields pasted into SEARCH_INDEX — gives the global search box access to
## free-text columns that are not shown as primary columns
drug_search_cols <- c(
  "nci_concept_definition", "disease_indication",
  "atc_level1", "atc_level2", "atc_level3",
  "drug_cancer_relevance"
)
drug_target_search_cols <- c(drug_search_cols, "target_genename")

biomarker_search_cols <- c(
  "evidence_description", "molecular_profile_name",
  "therapeutic_context", "evidence_url", "biomarker_source"
)
```

<br><br>

# Installation

```{r}
#| label: install
#| echo: true
#| eval: false

if (!("remotes" %in% installed.packages())) {
  install.packages("remotes")
}
remotes::install_github('sigven/pharmOncoX')
```

<br><br>

# Cancer drug classifications

## Targeted agents

Plotted below are key statistics with respect to drug classification
numbers for targeted and chemotherapy agents found in _pharmOncoX_.
Existing drug classifications have been retrieved from
[ATC](https://www.whocc.no/), and these have been extended with manual
addition/curation, and also through the establishment of multiple novel
levels in the ATC tree, particularly for targeted therapies. Note that
only drugs that are indicated for cancer conditions (as harvested from
the Open Targets platform) are considered in the numbers plotted below.

<br>

```{r}
#| label: targeted-agents
#| echo: false
#| output: false

drugs <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("targeted_therapy_classified",
                         "hormone_therapy_classified"),
  output_resolution = "drug",
  drug_action_inhibition = TRUE,
  drug_source_opentargets = TRUE)

drug_classifications <-
  drugs$records |>
  dplyr::select(drug_name, atc_level3) |>
  dplyr::mutate(
    atc_level3 = stringr::str_replace_all(
      atc_level3,
      "\\|(Antineovascularisation agents|Selective immunosuppressants)",
      ""
    )
  ) |>
  dplyr::group_by(atc_level3) |>
  dplyr::summarise(n = dplyr::n()) |>
  dplyr::mutate(pct = round(n / sum(n) * 100, digits = 2)) |>
  dplyr::arrange(dplyr::desc(pct)) |>
  dplyr::filter(n >= 2)

p_targeted_classifications <- ggplot2::ggplot(
  data = drug_classifications,
  ggplot2::aes(x = reorder(atc_level3, pct), y = pct)) +
  ggplot2::geom_bar(stat = "identity", fill = "steelblue") +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::ylab("Percent of targeted agents") +
  ggplot2::xlab("") +
  ggplot2::scale_y_continuous(breaks = seq(0, 12, 2)) +
  ggplot2::geom_text(
    ggplot2::aes(label = n), hjust = 1.4, vjust = 0.50,
    color = "white", size = 4) +
  ggplot2::theme(
    legend.title  = ggplot2::element_blank(),
    axis.text.x   = ggplot2::element_text(size = 14, vjust = 0.5),
    legend.text   = ggplot2::element_text(family = "Helvetica", size = 14),
    axis.text.y   = ggplot2::element_text(family = "Helvetica", size = 13),
    axis.title.x  = ggplot2::element_text(family = "Helvetica", size = 14),
    axis.title.y  = ggplot2::element_text(family = "Helvetica", size = 14)
  )
```

```{r}
#| label: p-targeted
#| echo: false
#| fig-width: 9
#| fig-height: 13
p_targeted_classifications
```

## Chemotherapy agents

```{r}
#| label: chemo-agents
#| echo: false
#| output: false

drugs <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("chemo_therapy_classified"),
  output_resolution = "drug",
  drug_classified_cancer = TRUE,
  drug_source_opentargets = TRUE)

drug_classifications_chemo <-
  drugs$records |>
  dplyr::select(drug_name, atc_level3) |>
  dplyr::group_by(atc_level3) |>
  dplyr::summarise(n = dplyr::n()) |>
  dplyr::mutate(pct = round(n / sum(n) * 100, digits = 2)) |>
  dplyr::arrange(dplyr::desc(pct))

p_chemo_classifications <- ggplot2::ggplot(
  data = drug_classifications_chemo,
  ggplot2::aes(x = reorder(atc_level3, pct), y = pct)) +
  ggplot2::geom_bar(stat = "identity", fill = "#E69F00") +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::ylab("Percent of chemotherapy agents") +
  ggplot2::xlab("") +
  ggplot2::scale_y_continuous(breaks = seq(0, 30, 5)) +
  ggplot2::geom_text(
    ggplot2::aes(label = n), hjust = 1.4, vjust = 0.50,
    color = "white", size = 4) +
  ggplot2::theme(
    legend.title  = ggplot2::element_blank(),
    axis.text.x   = ggplot2::element_text(size = 14, vjust = 0.5),
    legend.text   = ggplot2::element_text(family = "Helvetica", size = 14),
    axis.text.y   = ggplot2::element_text(family = "Helvetica", size = 13),
    axis.title.x  = ggplot2::element_text(family = "Helvetica", size = 14),
    axis.title.y  = ggplot2::element_text(family = "Helvetica", size = 14)
  )
```

```{r}
#| label: chemo-plot
#| echo: false
#| fig-width: 9
#| fig-height: 6
p_chemo_classifications
```

<br><br>

# Retrieval of drugs - examples

## Get BRAF-targeted drugs, list records per indication

```{r}
#| label: braf-drugs-full
#| echo: true

drugs <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("targeted_therapy_classified",
                         "targeted_therapy_unclassified"),
  drug_target = c('BRAF'))

## Number of drug records
nrow(drugs$records)

## Column names of drug records
colnames(drugs$records)
```

<br><br>

## Get RAS-targeted drugs, list per drug target

```{r}
#| label: ras-inhibitors
#| echo: true
#| output: false

drugs_ras <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("targeted_therapy_classified"),
  drug_action_inhibition = TRUE,
  output_resolution = "drug2target")$records |>
  dplyr::filter(atc_level3 == "RAS inhibitors") |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", ")) |>
  dplyr::select(
    drug_id, drug_name, drug_type, molecule_chembl_id,
    drug_action_type, target_symbol, dplyr::everything())
```

<br>

```{r}
#| label: rt-ras-inhibitors
#| echo: false

bake_reactable(
  df = drugs_ras,
  primary_cols = c("drug_name", "drug_action_type",
                   "target_symbol", "drug_max_clinical_stage", "atc_level3"),
  styling_cols = drug_base_styling_cols,
  search_cols  = drug_target_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",        minWidth = 150),
    drug_action_type      = reactable::colDef(name = "Action type",      minWidth = 120),
    target_symbol         = reactable::colDef(name = "Target",           minWidth = 90),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",      minWidth = 90),
    atc_level3            = reactable::colDef(name = "Drug category",    minWidth = 150)
  )
)
```

<br><br>

## Get MEK inhibitors, list per drug only

```{r}
#| label: mek-inhibitors
#| echo: true
#| output: false

drugs_mek <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("targeted_therapy_classified"),
  drug_action_inhibition = TRUE,
  drug_source_opentargets = TRUE,
  output_resolution = "drug")$records |>
  dplyr::filter(atc_level3 == "MEK inhibitors") |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", "))
```

<br>

```{r}
#| label: rt-mek-inhibitors
#| echo: false

bake_reactable(
  df = drugs_mek,
  primary_cols = c("drug_name", "drug_type", "drug_action_type",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = drug_base_styling_cols,
  search_cols  = drug_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",        minWidth = 150),
    drug_type             = reactable::colDef(name = "Drug type",        minWidth = 120),
    drug_action_type      = reactable::colDef(name = "Action type",      minWidth = 120),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",      minWidth = 90),
    atc_level3            = reactable::colDef(name = "Drug category",    minWidth = 150)
  )
)
```

<br><br>

## Get immune checkpoint inhibitors, list per drug target

```{r}
#| label: ici
#| echo: true
#| output: false

drugs_ici <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("targeted_therapy_classified"),
  drug_source_opentargets = FALSE,
  drug_classified_cancer = TRUE,
  output_resolution = "drug2target")$records |>
  dplyr::filter(
    !is.na(atc_level3) &
      atc_level3 %in% c("PD-1/PDL-1 inhibitors",
                        "Other ICIs - LAG3 inhibitors",
                        "Other ICIs - TIGIT inhibitors",
                        "Other ICIs - CTLA4 inhibitors",
                        "Other ICIs")) |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", ")) |>
  dplyr::select(
    drug_id, drug_name, drug_type,
    target_symbol, target_genename,
    dplyr::everything())
```

<br>

```{r}
#| label: rt-ici
#| echo: false

bake_reactable(
  df = drugs_ici,
  primary_cols = c("drug_name",
                   "target_symbol", "target_genename",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = c(drug_base_styling_cols, "target_ensembl_gene_id",
                   "target_entrezgene", "target_type"),
  search_cols  = drug_target_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",        minWidth = 150),
    target_symbol         = reactable::colDef(name = "Target",           minWidth = 90),
    target_genename       = reactable::colDef(name = "Target gene name", minWidth = 160),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",      minWidth = 90),
    atc_level3            = reactable::colDef(name = "ICI class",        minWidth = 180)
  )
)
```

<br><br>

## Get immune checkpoint inhibitors indicated for lung cancer, list per drug-target entry

```{r}
#| label: ici-lung
#| echo: true
#| output: false

drugs_ici_lung <- get_drugs(
  cache_dir = cache_dir,
  output_resolution = "drug2target",
  treatment_category = c("targeted_therapy_classified"),
  drug_source_opentargets = TRUE,
  drug_indication_main = "Lung")$records |>
  dplyr::filter(
    !is.na(atc_level3) &
      atc_level3 %in% c("PD-1/PDL-1 inhibitors",
                        "Other ICIs - LAG3 inhibitors",
                        "Other ICIs - TIGIT inhibitors",
                        "Other ICIs - CTLA4 inhibitors",
                        "Other ICIs")) |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", ")) |>
  dplyr::select(
    drug_id, drug_name, drug_type,
    target_symbol, target_genename,
    dplyr::everything())
```

<br>

```{r}
#| label: rt-ici-lung
#| echo: false

bake_reactable(
  df = drugs_ici_lung,
  primary_cols = c("drug_name",
                   "target_symbol", "target_genename",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = c(drug_base_styling_cols, "target_ensembl_gene_id",
                   "target_entrezgene", "target_type"),
  search_cols  = drug_target_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",        minWidth = 150),
    target_symbol         = reactable::colDef(name = "Target",           minWidth = 90),
    target_genename       = reactable::colDef(name = "Target gene name", minWidth = 160),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",      minWidth = 90),
    atc_level3            = reactable::colDef(name = "ICI class",        minWidth = 180)
  )
)
```

<br><br>

## Get antimetabolite drugs

```{r}
#| label: antimetabolites
#| echo: true
#| output: false

drugs_antimetab <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = c("chemo_therapy_classified"),
  output_resolution = "drug")$records |>
  dplyr::filter(
    !is.na(atc_level2) &
      stringr::str_detect(atc_level2, "ANTIMETABOLITES")) |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", "))
```

<br>

```{r}
#| label: rt-antimetabolites
#| echo: false

bake_reactable(
  df = drugs_antimetab,
  primary_cols = c("drug_name", "drug_type", "drug_action_type",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = drug_base_styling_cols,
  search_cols  = drug_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",     minWidth = 150),
    drug_type             = reactable::colDef(name = "Drug type",     minWidth = 120),
    drug_action_type      = reactable::colDef(name = "Action type",   minWidth = 120),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",   minWidth = 90),
    atc_level3            = reactable::colDef(name = "Drug category", minWidth = 150)
  )
)
```

<br><br>

## Get taxanes

```{r}
#| label: taxanes
#| echo: true
#| output: false

drugs_taxanes <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = "chemo_therapy_classified",
  output_resolution = "drug")$records |>
  dplyr::filter(
    stringr::str_detect(atc_level3, "Taxanes")) |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", "))
```

<br>

```{r}
#| label: rt-taxanes
#| echo: false

bake_reactable(
  df = drugs_taxanes,
  primary_cols = c("drug_name", "drug_type", "drug_action_type",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = drug_base_styling_cols,
  search_cols  = drug_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",     minWidth = 150),
    drug_type             = reactable::colDef(name = "Drug type",     minWidth = 120),
    drug_action_type      = reactable::colDef(name = "Action type",   minWidth = 120),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",   minWidth = 90),
    atc_level3            = reactable::colDef(name = "Drug category", minWidth = 150)
  )
)
```

<br><br>

## Get platinum compounds

```{r}
#| label: platins
#| echo: true
#| output: false

drugs_platins <- get_drugs(
  cache_dir = cache_dir,
  treatment_category = "chemo_therapy_classified",
  output_resolution = "drug")$records |>
  dplyr::filter(
    stringr::str_detect(atc_level3, "Platinum compounds")) |>
  dplyr::select(
    -c("drug_alias", "disease_main_group", "drug_clinical_id")) |>
  dplyr::mutate(
    disease_indication = stringr::str_replace_all(
      disease_indication, "\\|", ", ")) |>
  dplyr::select(
    drug_id, drug_name, drug_type, molecule_chembl_id,
    drug_action_type, opentargets, dplyr::everything())
```

<br>

```{r}
#| label: rt-platins
#| echo: false

bake_reactable(
  df = drugs_platins,
  primary_cols = c("drug_name", "drug_type", "drug_action_type",
                   "drug_max_clinical_stage", "atc_level3"),
  styling_cols = drug_base_styling_cols,
  search_cols  = drug_search_cols,
  col_defs_primary = list(
    drug_name             = reactable::colDef(name = "Drug name",     minWidth = 150),
    drug_type             = reactable::colDef(name = "Drug type",     minWidth = 120),
    drug_action_type      = reactable::colDef(name = "Action type",   minWidth = 120),
    drug_max_clinical_stage = reactable::colDef(name = "Max stage",   minWidth = 90),
    atc_level3            = reactable::colDef(name = "Drug category", minWidth = 150)
  )
)
```

<br><br>

# Retrieval of biomarkers

## Reported associations between BRCA1/2 alterations and drug sensitivity

* Get evidence from [CIViC](https://civicdb.org) and
  [CGI](https://www.cancergenomeinterpreter.org/biomarkers) for cancer
  drug sensitivity of BRCA1/2 alterations (somatically (tumor) or
  inherited/germline)

```{r}
#| label: biomarkers
#| echo: true
#| output: false

biomarkers <- get_biomarkers(cache_dir = cache_dir)

brca1_biomarkers <- list()
for (source in c('civic', 'cgi')) {
  brca1_biomarkers[[source]] <-
    biomarkers$data[[source]]$variant |>
    dplyr::filter(!is.na(symbol) & symbol %in% c("BRCA1", "BRCA2")) |>
    dplyr::group_by(variant_id, variant_name_primary, variant_consequence) |>
    dplyr::summarise(
      variant_alias = paste(variant_alias, collapse = ", "),
      .groups = "drop") |>
    dplyr::inner_join(
      biomarkers$data[[source]]$clinical, by = "variant_id") |>
    dplyr::select(
      variant_id, variant_name_primary, therapeutic_context,
      evidence_type, evidence_level,
      biomarker_source, biomarker_source_datestamp,
      molecular_profile_name, evidence_id, variant_origin,
      primary_site, evidence_id, source_id,
      evidence_url, evidence_description, clinical_significance) |>
    dplyr::distinct() |>
    dplyr::rename(
      literature_id = source_id,
      variant_name  = variant_name_primary) |>
    dplyr::filter(evidence_type == "Predictive") |>
    dplyr::select(
      variant_name, primary_site, therapeutic_context,
      molecular_profile_name, evidence_level,
      dplyr::everything())
}

brca1_biomarkers_all <-
  dplyr::bind_rows(
    brca1_biomarkers[['civic']],
    brca1_biomarkers[['cgi']]) |>
  dplyr::arrange(evidence_level)
```

<br>

```{r}
#| label: rt-brca-biomarkers
#| echo: false

bake_reactable(
  df = brca1_biomarkers_all,
  primary_cols = c("variant_name", "primary_site",
                   "therapeutic_context",
                   "clinical_significance", "molecular_profile_name"),
  styling_cols = c("variant_id", "evidence_id", "literature_id",
                   "biomarker_source_datestamp", "evidence_url",
                   "variant_origin", "evidence_type"),
  search_cols  = biomarker_search_cols,
  col_defs_primary = list(
    variant_name          = reactable::colDef(name = "Variant",           minWidth = 130),
    primary_site          = reactable::colDef(name = "Tumor type",        minWidth = 120),
    therapeutic_context   = reactable::colDef(name = "Drug/context",      minWidth = 150),
    clinical_significance = reactable::colDef(name = "Significance",      minWidth = 120),
    molecular_profile_name = reactable::colDef(name = "Molecular profile", minWidth = 160)
  )
)
```

<br><br>

# Session Info

```{r}
#| label: sessioninfo
#| eval: true
sessionInfo()
```

<br><br>

# References
